### 2022-08-04 ersteops/templates/printpdf/rendered_template.tex
add volatile files

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[spanish]{babel}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{eso-pic}
\usepackage{ifthen}
\usepackage[abs]{overpic}
\usepackage{pict2e,xcolor,varwidth}
\usepackage{color}
\usepackage{layout}
\usepackage[paperwidth=14cm, paperheight=22.5cm, left=0.0cm,right=0.5cm,top=3.3in,bottom=2.2in,headheight=3in,headsep=0pt,footskip=120pt]{geometry}
% Check parameters in: https://en.wikibooks.org/wiki/LaTeX/Page_Layout
%
\graphicspath{ {/vagrant/dev/petstore/static/img/printpdf/} }
\usepackage{fancyhdr}

@@

\pagestyle{fancy}
\fancyhf{}
% Define Header content
% fancyhead[C] image center
% fancyhead[L] image left
% fancyhead[L] image right
\fancyhead[C]{
    % Transparent head image
    \begin{overpic}[width=13.5cm,height=7cm,unit=1mm]{/vagrant/dev/petstore/templates/printpdf/transparent_head.png}
    % Hospital Logo
    % \put(10,45){
    %     % Logo Image
    %     hospital_logo.jpg
    % }
    % Consulta    
    % \put(68,65){\parbox[t]{6cm}{\textsf{\large{
    %    \textbf{Consulta \#:} 95
    % }
    % }}}    
    % Date    
    \put(68,65){\parbox[t]{6cm}{\textsf{\large{
       \textbf{Fecha:} 07, Jun 2018
    }
    }}}    
    % Patient
    \put(68,60){\parbox[t]{6cm}{\textsf{\large{
       \textbf{Paciente:} pelotitas
    }
    }}}
    % Species / Breed
    \put(68,50){\parbox[t]{6cm}{\textsf{\large{
       \textbf{Especie:} Gato / siames nordico
    }
    }}}
    % Sex
    \put(68,40){\parbox[t]{6cm}{\textsf{\large{
       \textbf{Sexo:} Hembra
    }
    }}}
    % weight
    \put(68,35){\parbox[t]{6cm}{\textsf{\large{
       \textbf{Peso:} 6.0
    }
    }}}
    % Dueño
    \put(68,30){\parbox[t]{6cm}{\textsf{\large{
       \textbf{Responsable:} Lillian Garcia
    }
    }}}
    % Edad
    \put(68,20){\parbox[t]{6cm}{\textsf{\large{
       \textbf{Edad:} 0 año,  meses
    }
    }}}
    % Diagnostico
    \put(10,5){\parbox[t]{10cm}{\textsf{\large{
       \textbf{Diagnostico Presuntivo:} esta es una nueva mascota de cero
    }
    }}}
    % Tratamiento
    \put(10,-5){\parbox[t]{10cm}{\textsf{\large{
       \textbf{Tratamiento:}
    }
    }}}                            
    % \put(70,42){\parbox[l]{4.2cm}{\textsf{\large{
    %    \textbf{Sexo:} Hembra
    % }
    % }}}
    % Pet Gender
    % \put(70,30){
    % \textsf{
    % \large{
    % \textbf{
    % Sexo:
    % }
    % Hembra
    % }
    % }
    % }
    % Pet weight
    % \put(70,25){
    % \textsf{
    % \large{
    % \textbf{
    % Peso:
    % }
    % 6.0
    % }
    % }
    % }        
    % % Informacion
    % \put(65,70){\parbox{4.2cm}{\textsf{
    %     Edad: Jan. 7, 2018
    % }}}
    % % Diagnostico
    % \put(10,16){\parbox{7cm}{\textsf{
    %     Diagnostico Presuntivo: esta es una nueva mascota de cero
    % }}}
    \end{overpic}
}
% End Header

% Begin Footer content
% fancyfoot[C] image center
% fancyfoot[L] image left
% fancyfoot[L] image right
\fancyfoot[L]{
    % Add grid param after unit to adjust text position over image
    % Transparent foot image
    \begin{overpic}[width=13.5cm,height=5cm,unit=1mm]{/vagrant/dev/petstore/templates/printpdf/transparent_foot.png}
    \put(1,5){
        \includegraphics[width=4cm, height=4cm]{qr_signature}
    }
    % Medic Signature
    % \put(50,33){\textsl{\textbf{\parbox[t]{2.4in}{
    %     {\fontfamily{frc}\selectfont
    %         \normalsize{ Medico Responsable: Juan ManuelRivero Mercado }
    %     }
    % }}}}
    % Medic
    \put(45,25){\parbox[t]{10cm}{\textsf{
       \textbf{Veterinario: } Juan Manuel Rivero Mercado
    }}}
    % Cedula
    \put(45,20){\parbox[t]{10cm}{\textsf{
       \textbf{Cedula Profesional: } 9999999999
    }}}
    \put(45,15){\parbox[t]{10cm}{\textsf{
        \textbf{ UNAM } 
    }}}
    % Medic Right
    % position <left, right(+5)>
    % \put(131,60){\textsf{\textsl{\parbox{2.65in}{
    %     
    % }}}}
    % % Telefono
    % \put(131,50){\textsf{\parbox{2.65in}{
    %     \textbf{Contacto} 
    % }}}
    % % Cedula Profesional
    % \put(131,40){\textsf{\parbox{2.65in}{
    %     \textbf{Cédula profesional} 
    % }}}
    % % Cedula Especialidad
    % \put(131,35){\textsf{\parbox{2.65in}{
    %     \textbf{Cédula especialidad} 
    % }}}
    % %Especialidad ,Alma Mater
    % \put(131.5,27){\textsf{\textbf{\parbox{2.65in}{
    %      , 
    % }}}}
    % % Sello electronico
    % \put(10,15){\textsf{
    %     \textbf{Sello electrónico:} 
    % }}
    % Footer prescrypto
    % Need try color here
    % \put(45,5){\textsf{\textbf{
    %     LAAM Vaterinarios
    % }}}
    \end{overpic}
}
% End footer
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist
\begin{document}
    % Include Background in ./prescript/media/media/template_v1.pdf
    \AddToShipoutPictureBG{\ifthenelse{\isodd{\value{page}}}{\includegraphics{laam_template}}{\includegraphics{laam_template}}}
    % Define page content
    \textsf{\large{
    \begin{changemargin}{1.5cm}{1.2cm}
        \begin{enumerate}
            \item \textbf{Bordetella[ Vacuna Canina]} \qquad dsd sdfsdf df sdf
        \end{enumerate}
        % Indicaciones Extra
        % \begin{enumerate}
        %     \textbf{Indicaciones Extra: \\ } \item \textbf{Bordetella[ Vacuna Canina]} \qquad dsd sdfsdf df sdf
        % \end{enumerate}
    \end{changemargin}
    }}
\end{document}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[spanish]{babel}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{eso-pic}
\usepackage{ifthen}
\usepackage[abs]{overpic}
\usepackage{pict2e,xcolor,varwidth}
\usepackage{color}
\usepackage{layout}
\usepackage[paperwidth=27.94cm, paperheight=21.59cm, left=0.0cm,right=0.0cm,top=0.0in,bottom=0.0in,headheight=0in,headsep=0pt,footskip=120pt]{geometry}
% Check parameters in: https://en.wikibooks.org/wiki/LaTeX/Page_Layout
%
\graphicspath{ {/vagrant/ersteops/static/img/printpdf/} }
\usepackage{fancyhdr}
%Definitions from inkscape
\makeatletter%
\providecommand\color[2][]{%
 \errmessage{(Inkscape) Color is used for the text in Inkscape, but the package 'color.sty' is not loaded}%
 \renewcommand\color[2][]{}%
}%
\providecommand\transparent[1]{%
 \errmessage{(Inkscape) Transparency is used (non-zero) for the text in Inkscape, but the package 'transparent.sty' is not loaded}%
 \renewcommand\transparent[1]{}%
}%
\providecommand\rotatebox[2]{#2}%
\newcommand*\fsize{\dimexpr\f@size pt\relax}%
\newcommand*\lineheight[1]{\fontsize{\fsize}{#1\fsize}\selectfont}%
\ifx\svgwidth\undefined%
 \setlength{\unitlength}{792bp}%
 \ifx\svgscale\undefined%
   \relax%
 \else%
   \setlength{\unitlength}{\unitlength * \real{\svgscale}}%
 \fi%
\else%
 \setlength{\unitlength}{\svgwidth}%
\fi%
\global\let\svgwidth\undefined%
\global\let\svgscale\undefined%
\makeatother%
\lineheight{1}%
\setlength\tabcolsep{0pt}%
%endDefinitions from inkscape

@@

\pagestyle{fancy}
\fancyhf{}
% Define Header content
% fancyhead[C] image center
% fancyhead[L] image left
% fancyhead[L] image right
\fancyhead[C]{
    % Transparent head image
    \begin{overpic}[width=13.5cm,height=7cm,unit=1mm]{/vagrant/ersteops/templates/printpdf/transparent_head.png}
    % Hospital Logo
    % \put(10,45){
    %     % Logo Image
    %     hospital_logo.jpg
    % }
    Consulta    
    \put(1,1){\parbox[t]{6cm}{\textsf{\large{
       \textbf{Consulta \#:} 1
    }
    }}}

    \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido}\end{tabular}}}}%

    % Date    
    \put(68,65){\parbox[t]{6cm}{\textsf{\large{
       %\textbf{Fecha:} 
    }
    }}}    
    % Patient
    \put(68,60){\parbox[t]{6cm}{\textsf{\large{
       %\textbf{Paciente:} 
    }
    }}}
    % Species / Breed
    \put(68,50){\parbox[t]{6cm}{\textsf{\large{
       %\textbf{Especie:}  / 
    }
    }}}
    % Sex
    \put(68,40){\parbox[t]{6cm}{\textsf{\large{
       %\textbf{Sexo:} 
    }
    }}}
    % weight
    \put(68,35){\parbox[t]{6cm}{\textsf{\large{
       %\textbf{Peso:} 
    }
    }}}
    % Dueño
    \put(68,30){\parbox[t]{6cm}{\textsf{\large{
       %\textbf{Responsable:} 
    }
    }}}
    % Edad
    \put(68,20){\parbox[t]{6cm}{\textsf{\large{
       %\textbf{Edad:}  año,  meses
    }
    }}}
    % Diagnostico
    \put(10,5){\parbox[t]{10cm}{\textsf{\large{
       %\textbf{Diagnostico Presuntivo:} 
    }
    }}}
    % Tratamiento
    \put(10,-5){\parbox[t]{10cm}{\textsf{\large{
       %\textbf{Tratamiento:}
    }
    }}}                            
    % \put(70,42){\parbox[l]{4.2cm}{\textsf{\large{
    %    \textbf{Sexo:} 
    % }
    % }}}
    % Pet Gender
    % \put(70,30){
    % \textsf{
    % \large{
    % \textbf{
    % Sexo:
    % }
    % 
    % }
    % }
    % }
    % Pet weight
    % \put(70,25){
    % \textsf{
    % \large{
    % \textbf{
    % Peso:
    % }
    % 
    % }
    % }
    % }        
    % % Informacion
    % \put(65,70){\parbox{4.2cm}{\textsf{
    %     Edad: 
    % }}}
    % % Diagnostico
    % \put(10,16){\parbox{7cm}{\textsf{
    %     Diagnostico Presuntivo: 
    % }}}
    \end{overpic}
}
% End Header

% Begin Footer content
% fancyfoot[C] image center
% fancyfoot[L] image left
% fancyfoot[L] image right
\fancyfoot[L]{
    % Add grid param after unit to adjust text position over image
    % Transparent foot image
    \begin{overpic}[width=13.5cm,height=5cm,unit=1mm]{/vagrant/ersteops/templates/printpdf/transparent_foot.png}
    \put(1,5){
        \includegraphics[width=4cm, height=4cm]{qr_signature}
    }
    % Medic Signature
    % \put(50,33){\textsl{\textbf{\parbox[t]{2.4in}{
    %     {\fontfamily{frc}\selectfont
    %         \normalsize{ Medico Responsable:  }
    %     }
    % }}}}
    % Medic
    \put(45,25){\parbox[t]{10cm}{\textsf{
       %\textbf{Veterinario: } 
    }}}
    % Cedula
    \put(45,20){\parbox[t]{10cm}{\textsf{
       %\textbf{Cedula Profesional: } 
    }}}
    \put(45,15){\parbox[t]{10cm}{\textsf{
        %\textbf{  } 
    }}}
    % Medic Right
    % position <left, right(+5)>
    % \put(131,60){\textsf{\textsl{\parbox{2.65in}{
    %     
    % }}}}
    % % Telefono
    % \put(131,50){\textsf{\parbox{2.65in}{
    %     \textbf{Contacto} 
    % }}}
    % % Cedula Profesional
    % \put(131,40){\textsf{\parbox{2.65in}{
    %     \textbf{Cédula profesional} 
    % }}}
    % % Cedula Especialidad
    % \put(131,35){\textsf{\parbox{2.65in}{
    %     \textbf{Cédula especialidad} 
    % }}}
    % %Especialidad ,Alma Mater
    % \put(131.5,27){\textsf{\textbf{\parbox{2.65in}{
    %      , 
    % }}}}
    % % Sello electronico
    % \put(10,15){\textsf{
    %     \textbf{Sello electrónico:} 
    % }}
    % Footer prescrypto
    % Need try color here
    % \put(45,5){\textsf{\textbf{
    %     LAAM Vaterinarios
    % }}}
    \end{overpic}
}
% End footer
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist
\begin{document}
    % Include Background in ./prescript/media/media/template_v1.pdf
    \AddToShipoutPictureBG{\ifthenelse{\isodd{\value{page}}}{\includegraphics{laam_template}}{\includegraphics{laam_template}}}
    % Define page content
    \textsf{\large{
    \begin{changemargin}{1.5cm}{1.2cm}
        \begin{enumerate}
            %
            bla!
        \end{enumerate}
        % Indicaciones Extra
        % \begin{enumerate}
        %     \textbf{Indicaciones Extra: \\ } 
        % \end{enumerate}
    \end{changemargin}
    }}
\end{document}
